### 2024-08-08 basic-statistics.qmd
20240807 - weighted quantile/median

If you want to give some values more weight to others, you can calculate a weighted mean and a weighted median (or other quantile), while assigning a weight to each value.

@@

```{r}
#mean(data, na.rm = TRUE)
#median(data, na.rm = TRUE)
#DescTools::HodgesLehmann(exampleValues, na.rm = TRUE)
#petersenlab::Mode(exampleValues)
#weighted.mean(data, weights, na.rm = TRUE)
#DescTools::Quantile(data, weights, na.rm = TRUE)
```

>>>>

If you want to give some values more weight to others, you can calculate a weighted mean and a weighted median (or other quantile), while assigning a weight to each value.
The [`petersenlab`](https://github.com/DevPsyLab/petersenlab) package [@R-petersenlab] contains various functions for computing the weighted median (i.e., a weighted quantile at the 0.5 quantile, which is equivalent to the 50th percentile) based on @Akinshin2023.
Because some projections are outliers, we use a trimmed version of the weighted Harrell-Davis quantile estimator for greater robustness.

@@

```{r}
#mean(data, na.rm = TRUE)
#median(data, na.rm = TRUE)
#DescTools::HodgesLehmann(exampleValues, na.rm = TRUE)
#petersenlab::Mode(exampleValues)
#weighted.mean(data, weights, na.rm = TRUE)
#petersenlab::wthdquantile(data, weights, probs = 0.5)
```
